PubCrawl: A Paper Search Engine

### 2012-05-15 report/paper.tex
Added emails :)

\documentclass[12pt]{article}
\setcounter{secnumdepth}{2}

\title{PubCrawl: A Paper Search Engine}
\author{Frank Li \\
Abhishek Sarkar \\
Manasi Vartak}
\date{May 16, 2012}

\usepackage{graphicx}

@@

A final variation on the basic scoring function is the incorporation of a damping factor $d$. A user following a citation chain will eventually stop, possibly at the end of the chain. Intuitively, the farther down a chain a user traverses, the less likely the papers will relevant and important to the original query, and the more likely the user will stop. The damping factor models this behaviour by reducing the change produced by the scoring function as the number of rounds increases. Adapted from PageRank, this results in the final version of our scoring function:\\
\begin{equation}
\label{eqn:damping}
S(p)= n(\frac{1-d}{N}+d(\Sigma_{c \in C} \frac{S(c)}{D(c)}+E(p)))
\end{equation}
where $d$ is the damping factor, $N$ is the total number of papers/nodes in the network, and all other variables remain as defined.

@@

MANASI'S WEBSITE STUFF//
%Manasi's website stuff

@@

\section{Acknowledgements}
\null

>>>>

\documentclass[12pt]{article}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{graphicx}

\setcounter{secnumdepth}{2}

\title{PubCrawl: A Paper Search Engine}
\author{Frank Li (frankli@mit.edu)\\
Abhishek Sarkar (aksarkar@mit.edu)\\
Manasi Vartak (mvartak@mit.edu)}
\date{May 16, 2012}

@@

A final variation on the basic scoring function is the incorporation of a
damping factor $d$. A user following a citation chain will eventually stop,
possibly at the end of the chain. Intuitively, the farther down a chain a user
traverses, the less likely the papers will relevant and important to the
original query, and the more likely the user will stop. The damping factor
models this behaviour by reducing the change produced by the scoring function
as the number of rounds increases. Adapted from PageRank, this results in the
final version of our scoring function:\\

\begin{equation}
\label{eqn:damping}
S(p)= n(\frac{1-d}{N}+d(\Sigma_{c \in C} \frac{S(c)}{D(c)}+E(p)))
\end{equation}

where $d$ is the damping factor, $N$ is the total number of papers/nodes in the
network, and all other variables remain as defined.

@@

%Manasi's website stuff

@@

\section{Acknowledgments}
\null
